### 2022-11-15 NSF2022/Description/broaderimpacts.tex
yny 1114h

\item Use machine learning to post-process data from the Janus particle self-assembly

\item Mathematically investigate self-assembly in the zero-screen-length limit
\end{enumerate}
The UR support is for eight summer weeks. In addition to collaborating
with the PI, they will have tutorials and receive training in
mathematical writing and presentation. The URs will have desks and
meeting room in a recently completed collaboration space built for the
Mathematics Department. As a condition of support, they will be required
to write a summary report and give a presentation in the university's
undergraduate research symposium. The PI will encourage the URs to
participate in a national conference.

To meaningfully engage the community, the PIs will prioritize students
coming from underrepresented groups and specifically target students
whose socio-economic background prevents them from participating in
out-of-state research experiences. PI Ryham will solicit applicants from
Fordham University's Collegiate Science and Technology Entry Program.
Students from the Bronx High School of Science (PI Ryham) and Newark
Science Park High School (PI Young) will also be encouraged to join the
research team. PI Quaife will work with undergraduates and high school
students through the Undergraduate Research Opportunity Program and
Young Scholar's Program, as he has done in the past.

To maximize vertical integration, the PIs and personnel will travel to
New York for one or two weeks during the summers. Finally, we will
create several modules to include in our courses. These modules will
introduce topics from numerical linear algebra and optimization and
highlight concrete applications of mathematics based on the ideas of the
proposal.

\section{Intellectual Merit}
\label{sec:IntellectualMerit}
The purpose of this research is to reach interesting physical phenomena
with less computational cost than molecular dynamics, and account for
more general features that continuum theory misses. The main ingredient
is defining a nonlocal interaction through the solution of an elliptic
boundary value problem that has the phenomenological characteristics of
long-range hydrophobic attraction. This minimal model, while intuitive,
is quite a general description of amphiphiles in solvent and gives rise
to rich phenomena from Janus particle aggregates to correctly predicting
elastic properties of bilayer. The technical research tasks include
quantifying collective properties of amphiphilic ensembles, improving on
mathematical models, efficient, high-order numerical algorithms for
large-scale simulations, and incorporating external fields through
electric charge.

>>>>

\item Use machine learning to post-process data from the granules self-assembly

\item Mathematically investigate self-assembly in the zero-screen-length limit
\end{enumerate}
The UR support is for eight summer weeks. In addition to collaborating
with PI Ryham, they will have tutorials and receive training in
mathematical writing and presentation. The URs will have desks and
meeting room in a recently completed collaboration space built for the
Mathematics Department. As a condition of support, they will be required
to write a summary report and give a presentation in the university's
undergraduate research symposium. PI Ryham will encourage the URs to
participate in a national conference.

To meaningfully engage the community, the PIs will prioritize students
coming from underrepresented groups and specifically target students
whose socio-economic background prevents them from participating in
out-of-state research experiences. PI Ryham will solicit applicants from
Fordham University's Collegiate Science and Technology Entry Program.
Students from the Bronx High School of Science (PI Ryham) and Newark
Science Park High School (PI Young) will also be encouraged to join the
research team.

PI Young has been actively involved with promotion of
underrepresented students at NJIT. One PhD student, Herve Nganguia, is
now an Assistant Professor at Towson University. PI Young has taught a
broad spectrum of courses in fluid mechanics and applied math modeling.
PI Quaife will work with undergraduates and high school
students through the Undergraduate Research Opportunity Program and
Young Scholar's Program, as he has done in the past.

%To maximize vertical integration, the PIs and personnel will travel to
%New York for one or two weeks during the summers. 
Finally, we will
create several modules to include in our courses. These modules will
introduce topics from numerical linear algebra and optimization and
highlight concrete applications of mathematics based on the ideas of the
proposal.

\section{Intellectual Merit}
\label{sec:IntellectualMerit}
This collaborative project focuses on modeling, simulation, and analysis
of self-assembly and collective dynamics of a suspension of granules with 
non-uniform hydrophobicity on their boundaries. The main
ingredient is a nonlocal interaction through the solution of moving
domain elliptic PDEs that encompasses long-range (non-additive) amphiphilic and
short-range steric interactions. The PIs have validated this
coarse-grained model against well-studied vesicle hydrodynamics. The
technical research tasks include quantifying collective properties of
ensembles of granules with tunable hydrophobicity, analyzing the mathematical model in 
distinguished limits to make connection with continuum models,
designing efficient and
high-order numerical algorithms for large-scale two- and
three-dimensional simulations with confinement, and developing a kinetic
theory to quantify the both the polar and nematic characteristics in the collective dynamics.
%
%The purpose of this research is to reach interesting physical phenomena
%with less computational cost than molecular dynamics, and account for
%more general features that continuum theory misses. The main ingredient
%is defining a nonlocal interaction through the solution of an elliptic
%boundary value problem that has the phenomenological characteristics of
%long-range hydrophobic attraction. This minimal model, while intuitive,
%is quite a general description of amphiphiles in solvent and gives rise
%to rich phenomena from Janus particle aggregates to correctly predicting
%elastic properties of bilayer. The technical research tasks include
%quantifying collective properties of amphiphilic ensembles, improving on
%mathematical models, efficient, high-order numerical algorithms for
%large-scale simulations, and incorporating external fields through
%electric charge.

### 2022-11-15 NSF2022/Description/priorsupport.tex
yny 1114h

\noindent
{\it Broader impacts:} 
One PhD student (Szu-Pei Fu) was funded to work with PI Young, and work
has resulted in seven papers~\cite{Nganguia2013_PoF, Nganguia2013_PRE,
Young2014_JFM, Young2015_PoF, Nganguia2015_CiCP, Pak2015_PNAS,
fu2015pre}. PI Young has been actively involved with promotion of
underrepresented students at NJIT. One PhD student, Herve Nganguia, is
now an Assistant Professor at Towson University. PI Young has taught a
broad spectrum of courses in fluid mechanics and applied math modeling.

@@

\begin{comment}
\begin{wrapfigure}[11]{r}{0.56\textwidth}
\vspace{-19pt}
%\definecolor{barblue}{RGB}{51,102,254}
%\renewcommand\sfdefault{phv}
%\renewcommand\mddefault{mc}
%\renewcommand\bfdefault{bc}
%\sffamily
\begin{ganttchart}[
    canvas/.append style={fill=none, draw=black!5, line width=.75pt},
        x unit =4.5mm,
        y unit chart =\baselineskip,
    hgrid style/.style={draw=black!5, line width=.75pt},
    vgrid={*1{draw=black!5, line width=.75pt}},
    title/.style={draw=none, fill=none},
    title label font=\bfseries\footnotesize, % numbers across the top
    title label node/.append style={below=3pt},
    include title in canvas=false,
    bar label font=\mdseries\footnotesize\color{black!70}, 
    % titles across the left
    %bar label node/.append style={left=2cm},
    bar/.append style={draw=none, fill=blue},
    bar incomplete/.append style={fill=blue},
    bar progress label font=\mdseries\footnotesize\color{black!70},
    milestone label font=\mdseries\small\color{black!70},
        milestone left shift =0.9,
        milestone right shift =0.1,
        % Don't draw group bars
        group height =0,
        group peaks height =0,
        group label font =\bfseries\small,
]{1}{12}
\gantttitle[
    title label node/.append style={below left=3pt and -6pt}
]{QUARTERS:\quad1}{1}
\gantttitlelist{2,...,12}{1} \\
%\ganttgroup{Tasks\hfill}{1}{12}\\
\ganttbar[bar/.append style={fill=red}]{Specific Aim 1}{1}{12} \\
\ganttbar[bar/.append style={fill=blue}]{Specific Aim 2}{1}{12}\\
\ganttbar[bar/.append style={fill=green}]{Specific Aim 3}{1}{12}\\
\ganttbar[bar/.append style={fill=black}]{Program Management}{1}{12}
\ganttbar[bar/.append style={fill=magenta}]{}{4}{4}
\ganttbar[bar/.append style={fill=magenta}]{}{8}{8}
\ganttbar[bar/.append style={fill=magenta}]{}{12}{12}
\end{ganttchart}
\vspace{-10pt}
\caption{Schedule for the proposed work, measured in quarters from the
  beginning of the project. The lead PI of each Specific Aim will be
  Ryham (red), Quaife (blue), and Young (green). Project management will
  be continuous (black), but we anticipate extra attention will be
  necessary to align objectives in quarters 4, 8, and 12 (magenta).}
\label{fig:schedule}
\end{wrapfigure}
\end{comment}
\textbf{Project management}: 
%
The success of the proposed research requires complementary expertise
and collaborative efforts in physics, applied mathematics, and
scientific computing. PI Ryham has been working on mathematical modeling
with a strong analytical background. PI Young has been working on many
areas of computational fluid dynamics and applications to math biology
for many years. PI Quaife has been working on integral equation methods,
fast algorithms, and their applications to fluid dynamics for many
years.  Their recent collaborative works on the granule-based vesicles
in two dimensions~\cite{FuQuRyYo22, fu-ryh-qua-you2022} has provided a
solid foundation for the proposed research.

@@

\textbf{Collaboration plan}: 
%
The management responsibility of this collaborative research will reside
with PI Quaife. The research work is structured to meet the tasks
discussed in \S\ref{sec:proposed-work}. The PIs and students will meet
frequently on Zoom and in person when possible. PI Ryham and PI Young
will conduct biweekly meetings in person, with PI Quaife joining over
Zoom from Florida. The PIs will share software packages, paper sources,
and references on a common \textsf{Git} repository. The resulting
software packages will be posted on the \textsf{Github} software
repository.
%
%\smallskip
%
\textbf{Research Schedule:} The detailed schedule for the proposed work
is shown in Figure~\ref{fig:schedule}. Each PI will spearhead a
different Specific Aim, and program management will happen
throughout, with special coordination taken in quarters 4, 8, and
12.

>>>>

\noindent
{\it Broader impacts:} 
One PhD student (Szu-Pei Fu) was funded to work with PI Young, and work
has resulted in seven papers~\cite{Nganguia2013_PoF, Nganguia2013_PRE,
Young2014_JFM, Young2015_PoF, Nganguia2015_CiCP, Pak2015_PNAS,
fu2015pre}. 
%PI Young has been actively involved with promotion of
%underrepresented students at NJIT. One PhD student, Herve Nganguia, is
%now an Assistant Professor at Towson University. PI Young has taught a
%broad spectrum of courses in fluid mechanics and applied math modeling.

@@

\begin{comment}
\begin{wrapfigure}[11]{r}{0.56\textwidth}
\vspace{-19pt}
%\definecolor{barblue}{RGB}{51,102,254}
%\renewcommand\sfdefault{phv}
%\renewcommand\mddefault{mc}
%\renewcommand\bfdefault{bc}
%\sffamily
\begin{ganttchart}[
    canvas/.append style={fill=none, draw=black!5, line width=.75pt},
        x unit =4.5mm,
        y unit chart =\baselineskip,
    hgrid style/.style={draw=black!5, line width=.75pt},
    vgrid={*1{draw=black!5, line width=.75pt}},
    title/.style={draw=none, fill=none},
    title label font=\bfseries\footnotesize, % numbers across the top
    title label node/.append style={below=3pt},
    include title in canvas=false,
    bar label font=\mdseries\footnotesize\color{black!70}, 
    % titles across the left
    %bar label node/.append style={left=2cm},
    bar/.append style={draw=none, fill=blue},
    bar incomplete/.append style={fill=blue},
    bar progress label font=\mdseries\footnotesize\color{black!70},
    milestone label font=\mdseries\small\color{black!70},
        milestone left shift =0.9,
        milestone right shift =0.1,
        % Don't draw group bars
        group height =0,
        group peaks height =0,
        group label font =\bfseries\small,
]{1}{12}
\gantttitle[
    title label node/.append style={below left=3pt and -6pt}
]{QUARTERS:\quad1}{1}
\gantttitlelist{2,...,12}{1} \\
%\ganttgroup{Tasks\hfill}{1}{12}\\
\ganttbar[bar/.append style={fill=red}]{Specific Aim 1}{1}{12} \\
\ganttbar[bar/.append style={fill=blue}]{Specific Aim 2}{1}{12}\\
\ganttbar[bar/.append style={fill=green}]{Specific Aim 3}{1}{12}\\
\ganttbar[bar/.append style={fill=black}]{Program Management}{1}{12}
\ganttbar[bar/.append style={fill=magenta}]{}{4}{4}
\ganttbar[bar/.append style={fill=magenta}]{}{8}{8}
\ganttbar[bar/.append style={fill=magenta}]{}{12}{12}
\end{ganttchart}
\vspace{-10pt}
\caption{Schedule for the proposed work, measured in quarters from the
  beginning of the project. The lead PI of each Specific Aim will be
  Ryham (red), Quaife (blue), and Young (green). Project management will
  be continuous (black), but we anticipate extra attention will be
  necessary to align objectives in quarters 4, 8, and 12 (magenta).}
\label{fig:schedule}
\end{wrapfigure}
\end{comment}
\textbf{Project management}: 
%
The success of the proposed research requires complementary expertise
and collaborative efforts in physics, applied mathematics, and
scientific computing. PI Ryham has been working on mathematical modeling
with a strong analytical background. PI Young has been working on many
areas of fluid dynamics with applications to soft matters. 
PI Quaife has been working on integral equation methods,
fast algorithms, and their applications to fluid dynamics.  
Their recent collaborative works on the granule-based vesicles
in two dimensions~\cite{FuQuRyYo22, fu-ryh-qua-you2022} has provided a
solid foundation for the proposed research.

@@

\textbf{Collaboration plan}: 
%
PI Quaife is responsible for the overall management of the project.
The research work is structured to meet the tasks
in \S\ref{sec:proposed-work}. The PIs and students will meet
on Zoom and in person when possible. PI Ryham and PI Young
will conduct biweekly meetings in person, with PI Quaife joining over
Zoom from Florida. The PIs will share software packages, paper sources,
and references on a common \textsf{Git} repository. The resulting
software packages will be posted on the \textsf{Github} software
repository.
%
%\smallskip
%
\textbf{Research Schedule:} The detailed schedule for the proposed work
is shown in Figure~\ref{fig:schedule}. Each PI will spearhead a
Specific Aim, and program management will happen
throughout, with special coordination taken in quarters 4, 8, and
12.
